OSMAC_Method; Model: `r params$Model_Path`; 

### 2023-02-08 Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
identical type files updated for increasing r0 values

---
title: "OSMAC_Method; Model: `r params$Model_Path`; "
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

>>>>

---
params:
  Model_Path:
title: "OSMAC_Method; Model: `r params$Model_Path`; "
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---
